Parallel Adaptive Importance Sampling

### 2016-06-02 PAIS.tex
further elaboration on proposal distribution in section 6.3.2

% modifications to algorithm + spikes
In this problem we modify our PAIS algorithm to use a mixture of Gamma
distributions in the proposal distribution instead of a Gaussian
mixture. The PAIS-LA algorithm uses the Langevin proposal distribution
from the standard MALA algorithm with a pertubation taken from a Gamma
distribution with mean $X+\frac{1}{2}\beta^2\nabla \log\pi(\cdot)$,
and  variance $\beta^2$. Similarly we use a Gamma proposal in the MH
algorithm. This ensures that we only propose positive
parameters. Having a heavier right tail in the proposal distribution
also means that the posterior is absolutely continuous with respect to
the proposal. When this is not the case, the weight function can tend
to zero or infinity when $k_i \rightarrow \infty$, which results in
poor, very spiky approximations of the tails of the posterior distribution leading to slow convergence.

>>>>

% modifications to algorithm + spikes
In this problem we modify our PAIS algorithm to use a mixture of Gamma
distributions in the proposal distribution instead of a Gaussian
mixture. The PAIS-Gamma and MH-Gamma algorithms use a Gamma
proposal distribution with mean centred at the previous state,
\[
	Y \sim \text{Gamma}(\cdot;\alpha^*, \beta^*) \quad \text{where} \quad \frac{\alpha^*}{\beta^*} = X \ \text{and} \ \frac{\alpha^*}{(\beta^*)^2} = \beta^2.
\]

Similarly the PAIS-LA algorithm uses the Langevin proposal distribution
from the standard MALA algorithm with a pertubation taken from a Gamma
distribution,
\[
	Y \sim \text{Gamma}(\cdot; \alpha^*, \beta^*), \quad \text{where} \quad \frac{\alpha^*}{\beta^*} = X+\frac{1}{2}\beta^2\nabla\log\pi(X) \ \text{and} \ \frac{\alpha^*}{(\beta^*)^2} = \beta^2.
\]
This ensures that we only propose positive
parameters. Having a heavier right tail in the proposal distribution
also means that the posterior is absolutely continuous with respect to
the proposal. When this is not the case, the weight function can tend
to zero or infinity when $k_i \rightarrow \infty$, which results in
poor, very spiky approximations of the tails of the posterior distribution leading to slow convergence.
